### 2016-04-27 ch06-concl/conclusions.tex
Finished conclusions

  \subsection{Non-parametric estimation}

  \subsection{Initialization of parametric estimation}
  To obtain a parametric model estimate from measured data often requires solving a non-convex optimization problem.
  However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers, in particular for cases where a low \gls{SNR} is available yet a lot of measurements are available.
  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM} and \gls{RFIR}.
  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).

@@

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp ji\dW\Ts)}{\Sum_i  a_i \exp ji\dW\Ts }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} for complex coefficients.

>>>>

  \subsection{Non-parametric estimation}
  Different non-parametric estimators, specifically from the family of local estimators, i. e. \gls{LRIC}, \gls{LRM} and \gls{LPM} are compared in this work.
  It has been shown that the most general \gls{LRIC} is very sensitive to the use of the `correct' local model order.
  The pre-existing \gls{LRM} and \gls{LPM}, however, are not as sensitive.
  It has been shown that the inherent bias of the \gls{LRM} becomes the dominant source of errors, in contrast to the variance, when an \gls{SNR} of less than $20\unit{dB}$ is available in the frequency bands of interest.
  For resonant systems, the \gls{LRM} is superior to the \gls{LPM} in terms of both bias and \gls{RMS} error in almost all cases.
  The \gls{LPM} is slightly superior for very noisy datasets ($\SNR < 20 \unit{dB}$) that have a very limited frequency resolution.

  It has also been illustrated that the use of such local models allows to extract the resonance peak and thereby the $\Hinf$ gain of a system.
  In that setting, the \gls{LPM} is not reliable due to its limited model flexibility.
  The \gls{LRM}, on the other hand, has been shown to be yield estimates of the $\Hinf$ gain that improved greatly compared to pure \gls{FRF} measurements.
  For systems that consist of complex dynamic behavior, this allows one to extract reasonable peak values without the hassle of building a global parametric model.
  The use of such local models, in practice, has been validated and can provide good estimates using a dataset that is four times smaller than what would be required for other \gls{FRF}-based methods.
  As such, the measurement time (and hence cost) can also be reduced by the same amount.

  \subsection{Initialization of parametric estimation}
  To obtain a parametric model estimate from measured data often requires solving a non-convex optimization problem.
  However, for such optimization problems, often an initial parameter estimate is required to allow convergence to the global optimum, or a local optimum nearby.
  In this thesis, it was investigated whether convergence to a good optimum can be attained more easily by means of \gls{FRF} smoothers, in particular for cases where a low \gls{SNR} is available yet a lot of measurements are available.
  A few practical smoothers have been studied, i.e. the time-truncated \gls{LPM} and \gls{RFIR}.
  It has been shown that especially the \gls{RFIR} provides smoothed \glspl{FRF} that aid in convergence to a good optimum than the existing state-of-the-art initializers (\gls{BTLS} and \gls{GTLS}).
  These smoothers allow one to obtain good models from noisier data than what existing techniques.
  The improvement of the initial values has been verified both on simulations, measurements and a simulation stress test consisting of different filters.
  While overall the \gls{RFIR} provides the best starting values from the different smoothers, combining multiple initial values remains a very valuable approach to make a system identification toolbox robust for the measurement data.

@@

    Specifically for the \gls{LRM}, currently a model structure that is equivalent to rational forms in continuous time, i.e. the (local) transfer function model is isomorphic with
    \begin{equation}
      \LocalModel[\CT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \dW^{i}}{\Sum_i  a_i \dW^{i}}
    \end{equation}
    There have already been some experiments with other model structures such as local discrete time models where
    \begin{equation}
      \LocalModel[\DT]{G}(\dW) 
      = \frac{\LocalModel{B}(\dW)}{\LocalModel{A}(\dW)}
      = \frac{\Sum_i  b_i \exp ji\dW\Ts)}{\Sum_i  a_i \exp ji\dW\Ts }
    \end{equation}
    but these have proven more difficult to estimate numerically and hence unreliable.
    A possible approach for this would be to use orthogonal polynomials~\citep{Forsythe1957,Bultheel2005} with complex coefficients.
